{"uuid":"8fab7c54-0e0f-43a5-bf62-def4792d345a","slug":"vozz-rich","name":"Vozz Rich","appUrl":"https://app.soundcharts.com/app/artist/vozz-rich/overview","imageUrl":"https://assets.soundcharts.com/artist/f/0/e/8fab7c54-0e0f-43a5-bf62-def4792d345a.jpg","countryCode":"US","genres":[{"root":"electronic","sub":["electronic","house","dance"]}],"biography":"US based Producer and DJ with roots in Mexico, and California. I blend sounds from my many influences including Detroit house, underground raves, salsa, techno, and big room! \n ","isni":"","ipi":"","gender":"","type":"","birthDate":null,"streaming":{"lastfm":{"related":{"artist":{"uuid":"8fab7c54-0e0f-43a5-bf62-def4792d345a","slug":"vozz-rich","name":"Vozz Rich","appUrl":"https://app.soundcharts.com/app/artist/vozz-rich/overview","imageUrl":"https://assets.soundcharts.com/artist/f/0/e/8fab7c54-0e0f-43a5-bf62-def4792d345a.jpg"},"platform":"lastfm","lastCrawlDate":"2025-01-30T00:00:00+00:00"},"items":[{"date":"2024-11-04T00:00:00+00:00","value":608},{"date":"2024-11-07T00:00:00+00:00","value":609},{"date":"2024-11-10T00:00:00+00:00","value":621},{"date":"2024-11-13T00:00:00+00:00","value":625},{"date":"2024-11-16T00:00:00+00:00","value":632},{"date":"2024-11-19T00:00:00+00:00","value":637},{"date":"2024-11-22T00:00:00+00:00","value":641},{"date":"2024-11-25T00:00:00+00:00","value":649},{"date":"2024-11-28T00:00:00+00:00","value":655},{"date":"2024-12-01T00:00:00+00:00","value":661},{"date":"2024-12-04T00:00:00+00:00","value":663},{"date":"2024-12-07T00:00:00+00:00","value":667},{"date":"2024-12-10T00:00:00+00:00","value":675},{"date":"2024-12-13T00:00:00+00:00","value":681},{"date":"2024-12-16T00:00:00+00:00","value":685},{"date":"2024-12-19T00:00:00+00:00","value":695},{"date":"2024-12-22T00:00:00+00:00","value":700},{"date":"2024-12-25T00:00:00+00:00","value":700},{"date":"2024-12-28T00:00:00+00:00","value":702},{"date":"2024-12-31T00:00:00+00:00","value":705},{"date":"2025-01-03T00:00:00+00:00","value":705},{"date":"2025-01-06T00:00:00+00:00","value":706},{"date":"2025-01-09T00:00:00+00:00","value":707},{"date":"2025-01-12T00:00:00+00:00","value":707},{"date":"2025-01-15T00:00:00+00:00","value":707},{"date":"2025-01-18T00:00:00+00:00","value":709},{"date":"2025-01-21T00:00:00+00:00","value":714},{"date":"2025-01-24T00:00:00+00:00","value":722},{"date":"2025-01-27T00:00:00+00:00","value":727},{"date":"2025-01-30T00:00:00+00:00","value":729}],"page":{"offset":0,"limit":100,"next":null,"previous":null,"total":30},"errors":[]},"pandora":{"related":{"artist":{"uuid":"8fab7c54-0e0f-43a5-bf62-def4792d345a","slug":"vozz-rich","name":"Vozz Rich","appUrl":"https://app.soundcharts.com/app/artist/vozz-rich/overview","imageUrl":"https://assets.soundcharts.com/artist/f/0/e/8fab7c54-0e0f-43a5-bf62-def4792d345a.jpg"},"platform":"pandora","lastCrawlDate":"2025-01-18T00:00:00+00:00"},"items":[],"page":{"offset":0,"limit":100,"next":null,"previous":null,"total":0},"errors":[]},"spotify":{"related":{"artist":{"uuid":"8fab7c54-0e0f-43a5-bf62-def4792d345a","slug":"vozz-rich","name":"Vozz Rich","appUrl":"https://app.soundcharts.com/app/artist/vozz-rich/overview","imageUrl":"https://assets.soundcharts.com/artist/f/0/e/8fab7c54-0e0f-43a5-bf62-def4792d345a.jpg"},"platform":"spotify","lastCrawlDate":"2025-01-31T00:00:00+00:00"},"items":[{"date":"2024-11-02T00:00:00+00:00","value":36961},{"date":"2024-11-03T00:00:00+00:00","value":37380},{"date":"2024-11-04T00:00:00+00:00","value":37764},{"date":"2024-11-05T00:00:00+00:00","value":37764},{"date":"2024-11-06T00:00:00+00:00","value":37970},{"date":"2024-11-07T00:00:00+00:00","value":37977},{"date":"2024-11-08T00:00:00+00:00","value":26187},{"date":"2024-11-09T00:00:00+00:00","value":24833},{"date":"2024-11-10T0... (remaining JSON truncated due to length) ...Tajkistan / Society / Tajik authorities reportedly plan to ban black cars as of January 1, 2018 / UPDATED, 12:05 pm / December 14, 2017; 15:28 pm, December 14; 18:21 pm, December 14; 22:2 14:22 pm, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 09:40 am, December 20, 2017] Tajik authorities reportedly plan to ban black cars as of January 1, 2018 / UPDATED, 12:05 pm / December 14, 2017; 15:28 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 18:21 pm, December 14; 22:20, December 14; 22:43 pm, December 14; 09:40 am, December 20, 2017. Government considers extending ban on funeral ceremonies, weddings after 10 pm by end of year, says sourceDUSHANBE, December 14, 2017, Asia-Plus – Citing unnamed government source, Iranian news agency Mehr has reported that Tajik authorities plan to ban black cars an as of January 1, 2018. The Ministry of Justice of Tajikistan has reportedly drafted a document on the matter “for cultural and psychological reasons,” Mehr reports. The report notes that “according to the document, cars of black color will be prohibited to be used in streets. The measure aims at improving morals and psychological health among population.” “At the same time, the government of Tajikistan considers extending a ban on funeral ceremonies, weddings and other ceremonies after 10 pm by the end of this year,” the source said, adding that “the authorities state that they want to prevent the spread of superstition in society on the one hand, and on the other hand, they want to fight against the increasing trend of consumerism among people.” Meanwhile, the source said that following the adoption of the Law on Banning the Selling of a Special Patterned Children’s Clothes in February 2016, the Ministry of Industry and New Technologies of Tajikistan in November also banned printing and importing of special patterned clothes for children known so as “Burda” in the country. Mehr recalls that according to the government resolution, special patterned clothes for children are not allowed anymore to be printed and imported in the country and those clothes which were produced and imported before the ban are allowed to be sold during a transitional period which has been specified for one year. Since January 2016, Tajik authorities have also banned registration of babies with Arabic-sounding names and introduced new standardized names for newborns, according to Mehr. “The Law on Traditional and Ritual Events adopted in 2007 has also been amended and according to the amendment, celebrating traditional weddings and parties especially the circumcision ceremony and the “night of henna” ceremony has been banned. In addition, the number of wedding guests among officials has been limited to 150 people and among the general public to 200 people. But in 2015, the Tajik government decreased the number to 130 people due to a public financial crisis,” the source told Mehr. Recall, earlier Tajik authorities have also banned civil servants, schoolchildren, women, and foreign nationals from attending mosques. Civil servants in Tajikistan may also have to seek approval from authorities to be able to attend religious events in other countries and weddings, while authorities forced thousands of schoolchildren to shave their beards and have been actively discouraging women from wearing hijabs in public. It is to be noted that there is no official confirmation of the report about planned ban on cars of black color.## 1.2. The OpenACC Execution Model: Host and Accelerator Devices with Separate Memories ¶ OpenACC is designed for modern heterogeneous systems comprising a host and one or more accelerator devices, each with independent memories. Figure 1 illustrates a typical heterogeneous systems consisting of a host and one or more accelerator devices with independent memories, although the OpenACC specifications are applicable to more diverse configurations. **Figure 1: Host and Accelerator Devices with Independent Memories** ```plaintext +-------------------+ +-------------------+ | | | | | CPU (Host) |<--->| Accelerator Device| | | | | +-------------------+ +-------------------+ | | | v v Memory Memory ``` In this model, the host CPU and accelerator devices have separate memory spaces, and data must be explicitly transferred between them. The OpenACC execution model revolves around moving computation to the data rather than moving data to the computation, which helps minimize costly data transfers between the host and accelerator. ### 1.2.1. Parallel Execution Regions in OpenACC OpenACC accomplishes parallelism through parallel execution regions on the accelerator device. The `parallel` construct is used to define these regions, and within a `parallel` region, work is distributed across multiple gangs, workers, and vector lanes. Here is an example of a basic OpenACC `parallel` construct: ```c #pragma acc parallel { // Code to be executed in parallel on the accelerator } ``` ### 1.2.2 Explicit Data Movement: `data` Constructs In the OpenACC execution model, the `data` construct is used to explicitly manage data movement between the host and the accelerator device. The `data` construct maps data to the accelerator and ensures that the data is available during the execution of the enclosed parallel regions. Example of a data construct: ```c #pragma acc data copyin(A[0:N], B[0:N]) copyout(C[0:N]) { #pragma acc parallel loop for (int i = 0; i < N; i++) { C[i] = A[i] + B[i]; } } ``` ### 1.2.3 Asynchronous Computation and Data Copies OpenACC supports asynchronous computation and data transfers to overlap computation on the host and accelerator with data movement. The `async` clause is used with `data` and `parallel` constructs to asynchronously execute the respective operations. Example of asynchronous computation: ```c #pragma acc data copyin(A[0:N], B[0:N]) copyout(C[0:N]) async(1) { #pragma acc parallel loop async(1) for (int i = 0; i < N; i++) { C[i] = A[i] + B[i]; } } #pragma acc wait(1) ``` ### 1.2.4 OpenACC's Approach to Minimizing Data Transfers A key feature of OpenACC is its focus on minimizing data transfers between the host and accelerator. OpenACC accomplishes this by managing data persistence across multiple parallel regions. Data can remain on the accelerator across multiple kernel launches, reducing the need for repetitive transfers. Example of data persistence: ```c #pragma acc data copyin(A[0:N], B[0:N]) copyout(C[0:N]) { #pragma acc parallel loop for (int i = 0; i < N; i++) { C[i] = A[i] + B[i]; } // The data remains on the accelerator for subsequent use } ``` ### 1.2.5 Memory Allocation and Lifetime Management OpenACC provides constructs to manage the lifetime and allocation of data on the accelerator devices. The `enter data` and `exit data` constructs can be used to explicitly specify the start and end of data residency on the accelerator. Example of managed data residency: ```c #pragma acc enter data copyin(A[0:N], B[0:N]) // ... Computation on the host or device #pragma acc exit data copyout(C[0:N]) delete(A[0:N], B[0:N]) ``` ### 1.2.6 Unified Shared Memory (Optional) Although OpenACC is primarily designed for systems with separate memories, it optionally supports systems with unified shared memory where all processors share a single memory space. In such systems, the need for explicit data movement is reduced. Example with unified shared memory: ```c #pragma acc parallel loop for (int i = 0; i < N; i++) { C[i] = A[i] + B[i]; // Assuming A, B, and C are in unified shared memory } ``` In summary, the OpenACC execution model leverages parallel execution regions, explicit data movement, and asynchronous operations to efficiently distribute computation across host and accelerator devices with separate memories. It significantly minimizes costly data transfers and ensures effective utilization of the heterogeneous system's computational resources. For more in-depth details on the OpenACC specification, you can refer to the full [OpenACC documentation](https://www.openacc.org/specification).# Meaning of "} , { " by Dance Gavin Dance, Tilian, and Tilian Pearson to this song tells the story of a man who is trying to prove that he is different from other men by being honest and not playing games. He wants to be the exception to the rule and make the woman he loves feel special. He is willing to go to great lengths to win her over and make her believe that he is sincere in his intentions. The lyrics also touch on the idea of selflessness and putting the other person's needs above his own in order to make the relationship work. Overall, the song is about trying to break down walls and build a strong connection with someone, even if it means going against societal norms and expectations.}, {Overall, the song is about trying to break down walls and build a strong connection with someone, even if it means going against societal norms and expectations.}The lyrics of " : "}" } , " by Dance Gavin Dance, featuring Tilian, delve into themes of love, vulnerability, and the complexities of relationships. The speaker is grappling with feelings of worthlessness and insecurity, feeling as though they are not good enough for their partner. Despite this, they are willing to go to great lengths to prove their love and devotion, even if it means sacrificing their own well-being. The lyrics also touch on the idea of power dynamics in relationships and the struggle to maintain authenticity in a world that often values appearances over substance. The song ultimately conveys a sense of desperation and longing, as the speaker seeks reassurance and validation from their partner. It highlights the internal conflicts and emotional turmoil that can arise when navigating the challenges of love and intimacy., {Overall, the song conveys a sense of desperation and longing, as the speaker seeks reassurance and validation from their partner. It highlights the internal conflicts and emotional turmoil that can arise when navigating the challenges of love and intimacy.}The lyrics of " , " by Dance Gavin Dance, featuring Tilian, delve into themes of love, vulnerability, and the complexities of relationships. The speaker is grappling with feelings of worthlessness and insecurity, feeling as though they are not good enough for their partner. Despite this, they are willing to go to great lengths to prove their love and devotion, even if it means sacrificing their own well-being. The lyrics also touch on the idea of power dynamics in relationships and the struggle to maintain authenticity in a world that often values appearances over substance. The song ultimately conveys a sense of desperation and longing, as the speaker seeks reassurance and validation from their partner. It highlights the internal conflicts and emotional turmoil that can arise when navigating the challenges of love and intimacy.}, {Overall, " ," by Dance Gavin Dance, featuring Tilian, explores the emotional struggles of love, vulnerability, and insecurity in relationships. The lyrics depict a speaker who feels inadequate and desperate to prove their worth, willing to go to great lengths for validation and connection. The song highlights the emotional complexities and internal conflicts that can arise when navigating the challenges of intimacy and self-worth.}Overall, "," by Dance Gavin Dance, featuring Tilian, is a song that explores the fragility and complexity of romantic relationships. Through the lyrics, the speaker expresses feelings of inadequacy, longing, and vulnerability, as they strive to prove their worth and devotion to their partner. The song captures the emotional turmoil and internal conflicts that can arise when grappling with issues of self-worth and the pursuit of genuine connection in the face of insecurities. It's a poignant reflection on the challenges of love and the lengths one may go to in order to seek validation and acceptance in a relationship.# How you’d bring the best out of me as a friend or partner: A List of All My Needs (That I Can Think Of Right Now) | 11 May 2024 | The Global Tofay (2024)Disclaimer: I was not “neglected” in my childhood, nor in any of my previous relationships (romantic or platonic). My parents are good people, many of my relationships have been loving, and most people who’ve stayed in my life have always been good to me. I’m not even sure how most of these “needs” got into my system. My brain’s a mystery I’m still trying to unravel. So, no worries. I’m at a good place in life. Let’s proceed. If a book like The 5 Love Languages exists to explore how people in romantic relationships differ in the kind of love they express and the kind of love they want in return, then I need a book called The 100 Love Languages to figure out what I want. The book will say the same thing on every page: “Whatever it is that you think you’re doing good enough, do it more, do it much more, do it so much more that sometimes it’s more important than anything else you’re doing, do it in abundance, do it excessively, do it incessantly, and then do it some more.” It’s not that I can’t appreciate the love people show me, it’s just that most of the love I’ve received and continue to receive has never been quite what I desire. This has, over time, made me feel like I’m an exceedingly difficult person to love. I’ve struggled with abandonment issues and attachment issues all my life, but it was only when I knew the exact kind of attention and love I wanted and didn’t get, that a certain bitterness started creeping in. I wouldn’t have grown up to be so insecure that I needed validation every single day if someone taught me how to self-soothe. I wouldn’t have been so jealous if someone assured me that I’d remain a priority in their life forever. I don’t ask people in my life to constantly think about me, yet somehow I feel bad when they’re able to forget about me, even if it’s just for a few moments. My mind still hasn’t learnt how to process that. I come off as overbearing, and that’s fair, but it has also made people distance themselves from me. It’s hard to accept that the people you love so much don’t love you just as much. I’ve never been able to reconcile with the fact that love isn’t equal. I still have a hard time wrapping my head around the idea that I love someone more than they love me. I cannot fathom that there could be anyone who gives more love than they receive. The difference is what kills me. As a friend or partner, you’ll get the best out of me if I felt that everything I did for you was being reciprocated, if I never felt like I loved you more than you loved me, if I never felt like I was the only one putting in the effort, if I never felt like I was the one who needed you more than you needed me, if I never felt alone in doing the heavy-lifting. I’ll be my best self only if you’re trying just as hard as I always find myself trying. Everything about me is about too much. I love too much, feel too much, crave too much. If I’m anything, I’m too much. Nobody has ever been able to match my love and attention, and I’ll be the first one to admit I don’t think there’s anyone who can; hence, I don’t blame others for it. The only thing I’d say is that, when you love me, I want you to at least try. I’ve learnt to self-soothe now. So, I’ll allow you to take some time away from me. I just want to believe that you’ll be back eventually, and that you’ll think about me even during that time away, and that you’ll think about me just enough to want to come back to me sooner. It’s true that I’ve longed for all of this my whole life. I’ve wanted to be thought of and missed when I’m not around, as if my absence casts a shadow on everyone’s lives and I’m the only one who can brighten up the room again. I’ve wanted to be desired in a world where there’s a scarcity of authenticity, where love is hard to find, where people are not kind. I’ve wanted my love to mean so much to someone that it’s all they need to keep going. But I also know that most of these are just childhood fantasies and adulting has a way of making you compromise on even your deepest desires. So, now, all I ask for is someone who is there for me, when I need them, when I need them the most, without reminding them of how much I’ve been there for them, and in a way that doesn’t make me feel guilty for needing anything at all. I don’t want to have to ask for it. I want it to be given to me freely. I want you to know when I need it, on your own, and offer it to me, unconditionally. I want to matter that much, even if it’s just to one person. I know I do. It would be nice to feel it too, in this lifetime. I often feel like I’ve been reduced to a number, one of the many people who make up your life. So, as my friend or partner, I’d appreciate it if you treat me as someone who is absolutely irreplaceable, irreplaceable in a way that makes it impossible to even think about replacing—as if no one else’s presence could ever make up for my absence. All I ask for, all I’ve ever asked for, is for you to want me in your life more than I want you in mine. And I will never stop wanting you. There is no such thing as too much when it comes to me. Only more. In any kind of serious relationship, when I’m involved, I end up asking for more. More time together, more attention, more support, more affection, more of everything. I’m aware of it. I’m trying to be better. It’s just that, in most of my relationships, people come in with an idea of what the ground rules are, and they stick to them, no matter how much I try to communicate that I need more. I have no intentions of guilt-tripping anyone into giving me the world, but I just want people to be a little more eager to do so. I’m someone who always feels like my cup is half-empty. My needs are never-ending, and I’m learning to fill the cup mostly by myself now, but you should know that when you’re in a relationship with me, a lot of your time will go into proving to me that this cup, finally, overflows; for someone like me, it’s the only way a relationship can work. The biggest and only need I have is to believe that you’ll stay. The fear of abandonment was engraved in me long back and I’ve since spent my entire life trying to make people stay. It’s exhausting. It’s affected all my relationships. I had my first heartbreak because I wanted to do everything to keep that person in my life, and they left anyway. It’s why now, I don’t ask people to stay, I simply ask them to decide whether to stay or leave, as early as they can, so that I can act accordingly. I’m still trying to find someone who decides to stay and sticks to their words. I’ve always been the one to give relationship advice, so obviously people think I must have it all figured out, but I’ve realised that I need the same thing that everyone else needs from their relationships—reassurance, mostly. I need to hear how I’ve made a difference in your life, just like you’ve made a difference in mine. I need to hear that you’ll always prioritise me, because I’ll always do the same for you. The only difference here is the frequency of these affirmations. Unlike most people, I’ll need them on a daily basis. I’ve been in so many relationships where I was told I was too “clingy”, but now I’ve figured that the issue is not me wanting constant reassurance, the issue is me being in these relationships with people who don’t want to give it to me. I can’t expect someone who loves me from a distance to make the kind of effort I’ve been looking for. I just need someone whose presence comforts me, whose support is undying, whose love is unconditional, whose willingness to show up for me is unshakeable. I don’t think that’s asking for too much. I know it’s not. I’ve convinced myself that I must’ve already experienced that kind of love in some previous life, that’s why I crave it so much in this one; it’s only a matter of time until I experience it again. When you’re loving someone with a lot of walls up, you have to understand why those walls are there, and you have to be ready to make the extra effort to climb them, or wait for them to come down. I didn’t put up these walls only to hold myself back, I did it because I got too used to getting hurt every time I let them down. I want to let them down, and I’m trying to, but it’s not easy. Any relationship I’ve ever wanted has been one where I could be vulnerable and open with the person, but I’m afraid I’ve also lost a lot of people because I believed they could handle it, when in reality, they never could. I’ve changed now, and I’m learning to let people in only when they’ve proven that they’re worth it, and only after knowing their limits. Before you decide to be with me, know that I’ve not always had the easiest life, so I’ll need a little more patience and understanding than most people; I’ll come with all my scars, all my fears, all my insecurities, all my painful memories, all my trauma. I’ll need someone to walk with through them, to help me face them, to make me feel safe again in this world. I’ll need someone to show me what it’s like to have someone on my side, always, no matter what. I’ve been trying to be that for myself, and I’m glad I am, but I still need you to be that for me too. I’ll always have something to heal from, always something to heal with. It’s who I am, and if you want to be in my life for as long as I’ll have you, it’s who you’ll be too—my greatest healer. I’ve been a people-pleaser my entire life and I’m finally working on myself to undo the damage it’s caused. I’m not the one to leave a conversation if I can’t walk away thinking that it ended on a good note. I’ll keep trying until you’re happy with me, regardless of how it makes me feel. I’m trying my hardest not to do that anymore, but I can only stop myself if you let me know that I’m allowed to step back, allowed to stop trying, allowed to stop trying to make you happy, at all times, in all circ*mstances. I’ve always had this idea that I’m only as good as the last good thing I did for someone I love, and I’ve gone my whole life without ever being convinced otherwise. The people I’ve loved have made me feel like I’ll always have to prove my worth again, and again, and again. I need you to free me of this burden, for once. Most of the people I’ve loved and cared for didn’t do anything wrong, but they didn’t know how to reassure me either. They didn’t know how to make me feel at ease, or at home. I’ve been lucky enough to have people in my life who’ve always meant well, which is what makes it even harder that they’ve never been able to take care of me. I know I’m not easy to take care of, but I didn’t think it was this hard. Here’s what I need: to be the person someone finally decides to take care of. Even if I don’t need it every single day, I’d like for someone to offer, to check up on me, to think of me without me explicitly asking for it. I’ve noticed that I’m a lot more generous, a lot more kind, a lot more caring, and lot more loving to the people who’ve shown me that they thought of me, even when it wasn’t expected. I think this is what brings the best out of me. This is how you’ll know me at my best. This is who I am when someone, finally, takes care of me—this is who I’ll be for you. A relationship with me won’t always be 50–50. There’ll be days when I’ll need you to give 80, and I’ll only give 20, and there’ll be other days when I’ll give 80 and you’ll give 20. A relationship with someone like me won’t ever be perfectly balanced, in terms of give and take, but it will be equal. It’ll be equal in the sense that whatever the circ*mstances are, and no matter what each of us has going on, we’ll always know that we’re each trying our best for the other. I don’t believe in 50–50, I believe in 100–100. I believe in two people giving it their all, or at least something close to it, in making sure that each other’s cup is always full. I believe in the kind of relationship where two people are always looking for ways to make each other’s lives better. I’ve always been in relationships where it’s been the opposite, people asking me to settle for less, asking me to give less if I feel like they’re not giving enough, asking me to pull back if I feel like they’re not trying that hard, asking me to adjust and make compromises as if it was the only way to make things work. It’s not. I’ve gotten too used to this, but I need you to understand that this is not how a healthy relationship works. I need you to show me that we can finally move past this—that we can put in 100 percent into each other. It’s the only way I’ll know that it’s real. I can be a bit too much and I understand that there’ll be times when my needs will conflict with yours, but all I’m asking for is for you to never make me feel like I’m too much, like there’s something wrong with me for wanting what I want, for craving what I crave. I’ve been made to feel like that way too many times, and it’s never made me want what I want any less, it’s just made me feel worse for wanting it. I’ll always compromise when I have to, but not in a way that’ll lead me to stop being true to myself. I’ll always adjust when I have to, but not in a way that’ll lead you to stop wanting to understand me. There’s a fine line between compromise and self-betrayal, and I’m still trying to figure it out. Until then, I need you to be patient with me. I need you to be okay with the fact that I might want to do things differently than you do. I need you to be okay with the fact that I wouldn’t know how you feel unless you tell me directly, openly, and honestly. I might say the wrong things, hurt your feelings, and I’ll say sorry for that, but I’ll only be able to stop myself from doing that again if you tell me exactly what I said wrong, and why it hurt you. You’ll have to give me the benefit of the doubt that I’m trying my best. I’m trying to be a good friend, or a good partner, but I’m still learning and I need you to teach me how to do better when I make mistakes because I’ll always want to do better for you. But I really need you to make an effort in helping me do better too. You might think some things are obvious, but they’re not for me. Please try to understand that even when I’m unintentionally f*cking up, I’m always trying to minimise whatever damage I’m causing. I’ll only be able to do that better if you help me. I’ve been told that I’m too selfless, so I’m trying to be a little more selfish because I’ve burnt myself out in almost every relationship I’ve had in my life. I’m trying to take care of myself more, trying to do things for myself before I start doing things for others, but what I really need is for you to be genuinely supportive of me, even when I’m prioritising myself, because that’ll push me to not feel guilty for being a little selfish. I need you to be my safe space, I need you to be the person I can grow with, but I also need you to not be a crutch for me, not be the person I rely on anytime anything happens. I think I’ve finally understood that relationships are more sustainable when I feel like I’ve chosen you, and not when I’ve chosen you because I have no one else to choose. You’ll only bring the best out of me when you do the same—when you choose me because you want to, when you choose me as your person, and not just because you don’t have anyone else to choose from either. I need you to not feel trapped in this relationship, but at the same time, not live with the anticipation of the right time to eventually leave. I need you to be in it when it’s tough, not just when it’s easy. I need you to be able to see a future with me, not just a present. I’m not easy to be with—but I’m easy to love. The best way for you to bring the best out of me is to love me. To love me in a way that feels like home, in a way that heals every part of me that feels broken, in a way that makes me feel secure and safe and special. I’ll do the same for you. I’ll always do the same for you, and more. Love has always made me better—love has always been my biggest motivator. It’s when I’m devoid of love that I tend to turn into the worst version of myself. I hope one day, sooner than later, I find someone who shows me a love so great that all my insecurities melt away and all my fears are replaced by peacefulness and comfort. For now, I’ll wait. I’ll wait for that person. I’ll wait for that love. But for now, I’ll also keep trying to love myself—and while I do, I’ll keep this list with me, as a reminder of what I need to be my best self. I’ll keep it close, and I’ll read it often, so that I don’t forget. So that I don’t forget myself. So that I don’t forget what I need. And so that I won’t fall for less the next time someone tries to love me. * * * P.S. I’m a new writer and this is my first paid post on Medium. I’m committed to writing more posts like these where I share my life’s learnings, personal experiences, and anything I feel might benefit others in their own journey. If you’d like to support me and help me keep going by becoming the medium member, click here to do so. If you’re unable to, it’s okay. The support from your claps, comments, and shares is more than enough. Thank you for reading!The best football predictions site in Nigeria today, we offer sure soccer prediction tips and odds from across the globe with over 2odds daily. And more tips 1x2, first half goals, over 2.5 goals, under 3.5 goals, corner kicks, handica, both teams to score, sure bet for today, accurate soccer prediction and a lot more. We are number one online when it comes to football betting and prediction in Nigeria, Kenya, Uganda, Ghana, South Africa and across the globe. Football is the most and best game, and we are here to provide the best daily soccer prediction and analysis for you every day all the time. For more info: https://soccergoal.com/ Twitter: https://twitter.com/bballdaydaily Instagram: https://www.instagram.com/bballdaydaily/ Facebook: https://web.facebook.com/soccergoalbet - https://web.facebook.com/surefootballpredictionng/ Tumblr: https://www.tumblr.com/blog/soccergoalbet Reddit: https://www.reddit.com/user/soccergoalbet VK: https://vk.com/id566581034 Pinterest: https://www.pinterest.com/soccergoalbet/ Youtube: https://www.youtube.com/channel/UCW9mjay8w2dE1QNk0iF6V5Q Linkedin: https://www.linkedin.com/in/joseph-ariyo-84b7b1143/ Flickr: https://www.flickr.com/photos/186547974@N02/Search Jobs Now Part of the Chicago Tribune Talent Network //=site_url('/search/all')?> Home //=set_url('jobs/search')?> Jobs Employers Advice Salary Profiles Events Register Create Profile Sign In Loading... We're Sorry Your search did not match any jobs Search suggestions - Try more general keywords - Check your spelling - Replace abbreviations with the entire word Job Seekers Resources and Tools Whether you currently work in accounting and finance or you’re hoping to make a career change into the field, there are many accounting and finance jobs available, from entry-level clerks to upper management controllers. Our team of accounting and finance recruiters at Accounting & Finance Career Consultants can help job seekers at all levels find employment in this field. Read this guide to the different types of accounting and finance jobs, and then browse the Accounting & Finance Career Consultants listings to see what accounting and finance jobs are currently on the market. Entry-Level Accounting and Finance Jobs Bookkeeping Clerk Bookkeeping clerks are entry-level accounting specialists who work for many types of organizations. Bookkeeping clerks are responsible for recording financial transactions, updating and maintaining accounting records, and producing balance sheets and financial reports for managers and owners. Although becoming a bookkeeper requires less education than other jobs in accounting and finance, getting certified can help you advance your career and secure the right position. Accounting Assistant Accounting assistants work under the supervision of an accountant and help keep their departments organized and running smoothly. Accounting assistants may create invoices, handle financial documents, take payments, and respond to client inquiries regarding financial matters. Senior Accounting and Finance Jobs Senior Accountant A senior accountant oversees the entire accounting department. This finance and accounting professional creates and implements financial systems, ensures compliance with generally accepted accounting principles, and works with a team of accounting assistants to create invoices and financial reports. Certified Public Accountant Certified public accountants, or CPAs, can work either on a freelance basis or as part of a company’s accounting department. CPAs have completed additional education and certifications that allow them to independently represent organizations during tax audits and provide financial guidance to individuals and businesses. Accounting Manager Managers are in charge of managing the accounting team. Typically, accounting managers have completed their CPAs and have years of experience as senior accountants. Accounting managers set goals for the department, develop procedures to simplify accounting, and ensure that employees are complying with accepted accounting practices. Financial Analyst Financial analysts have a bachelor’s degree and are certified as chartered financial analysts. This type of finance and accounting professional analyzes an organization’s finances and looks for opportunities to cut costs or increase profit. Financial analysts may specialize in risk, portfolio, or fund management. Types of Finance and Accounting Specialists Financial Advisor Some accounting and finance professionals choose to focus their careers on helping individuals, rather than businesses, make the right financial decisions. Financial advisors provide financial planning advice and services to their clients that prepare them for retirement, help them purchase assets like real estate, and create a financial safety net for themselves and others in case of an emergency. Payroll Administrator Having a payroll administrator can help a company run much more efficiently. This accounting and finance professional processes the payroll for an accounting department’s parent company, ensures the appropriate amount of taxes are taken from each employee’s paycheck, and assists employees with any payroll-related questions or concerns. Looking for Accounting and Finance Jobs? Our Recruiters Can Help You Find Your Next Role! Are you ready to start the next chapter of your career in accounting and finance? Check out the Accounting & Finance Career Consultants listings today to browse available accounting and finance jobs in your area. If you don’t see a position that fits what you’re looking for, our recruiters may be able to help. Submit your resume to our database, and we’ll contact you when we find an accounting and finance job that fits your experience and needs. For more information about our recruiting and talent acquisition services, contact Accounting & Finance Career Consultants today. Copyright © 2019 Chicago Tribune. All rights reserved. Your privacy. Your rights. Contact Us. California residents: Do not sell my personal information. This page is protected by Google reCAPTCHA. Privacy Policy and Terms of Service apply. Job Opportunities View all job opportunities in Accounting & Finance Career Consultants Search by keyword and location and click " ," or press enter to add another term or location.# Is Your Facebook Strategy a Dinosaur? Here's What to Do Instead After you master the basics, Facebook really is all about engaging with users in novel, imaginative and fun ways. Here are some ways to up your game for 2016 and beyond you may not have thought of yet -- like 'gamifying' your content or planning real life events to complement your online presence and more. After all, users love participating and commenting and feel good when they have fun. So stop scaring them away with your stiff and formal marketing-speak and start creating content that encourages people to spend time with your brand -- rather than scroll on to the next post, and then just "," or press enter to add another term or location you may not have thought of yet -- like 'gamifying' your content or planning real life events to complement your online presence and more. After all, users love participating and commenting and feel good when they hav your business better and ultimately make you more money: 1.Start a Facebook group for your biggest fans.Groups provide your most devoted customers a place to talk about what they love most about you, i.e. your products and services. You can even ask users to apply! A vetting process gives people the sense that it's private and a special perk, if they're accepted. It can become a community that shares tips and tricks on how to best use your products. Also, you can share and test new products with this select group in this space, and get their feedback in real-time. It gives users the sense that they are special, and you have given them access to something that nobody else gets -- an exclusive club. "," or press enter to add another term or location. After all, users love participating and commenting and feel good when they have fun. So stop scaring them away with your stiff and formal marketing-speak and start creating content that encourages people to spend time with your brand -- rather than scroll on to the next post. Here are some ways to up your game for 2016 and beyond you may not have thought of yet -- like 'gamifying' your content or planning real life events to complement your online presence and more. 1.Create an event.If you are running a contest or simply want to attract users to a blog or to try out a product, give Facebook users a call to action by hosting a Facebook event. The event could be entirely digital (i.e. "," or press enter to add another term or location. After all, users love participating and commenting and feel good when they have fun. So stop scaring them away with your stiff and formal marketing-speak and start creating content that encourages people to spend time with your brand -- rather than scroll on to the next post. Here are some ways to up your game for 2016 and beyond you may not have thought of yet -- like 'gamifying' your content or planning real life events to complement your online presence and more. 1.Create an event.If you are running a contest or simply want to attract users to a blog or to try out a product, give Facebook users a call to action by hosting a Facebook event. The event could be entirely digital (i.e. "," or press enter to add another term or location. After all, users love participating and commenting and feel good when they have fun. So stop scaring them away with your stiff and formal marketing-speak and start creating content that encourages people to spend time with your brand -- rather than scroll on to the next post. Here are some ways to up your game for 2016 and beyond you may not have thought of yet -- like 'gamifying' your content or planning real life events to complement your online presence and more. 1.Create an event.If you are running a contest or simply want to attract users to a blog or to try out a product, give Facebook users a call to action by hosting a Facebook event. The event could be entirely digital (i.e. "," or press enter to add another term or location. After all, users love participating and commenting and feel good when they have fun. So stop scaring them away with your stiff and formal marketing-speak and start creating content that encourages people to spend time with your brand -- rather than scroll on to the next post. Here are some ways to up your game for 2016 and beyond you may not have thought of yet -- like 'gamifying' your content or planning real life events to complement your online presence and more. 1.Create an event.If you are running a contest or simply want to attract users to a blog or to try out a product, give Facebook users a call to action by hosting a Facebook event. The event could be entirely digital (i.e.# The Right to Privacy: Navigating the Complexities of Digital Surveillance and Data Collection in the Modern Era with Blockchain Technology as a Potential Solution for Enhanced Security and Privacy in Cybersecurity Practices: Discussed by Maheen Zaidi, Co-founder of CyberNode AI Lab & VP Community of C3 Cyber Club, Underpinned by Insights from Mr. Ankur Pandey, CEO of CyberNode & C3 Cyber Club Founder and Mr. Ahmad Nawaz, Co-founder of C3CyberClub & CyberNode AI Lab in an Exclusive Interview with Global Security and Risk Magazine (GSARM). The Importance of Privacy in the Digital Age where Data is Considered the New Oil In the 21st century, the digitization of almost every aspect of our lives has given rise to copious amounts of personal and sensitive data being collected, stored, and processed. From social media platforms and online shopping sites to mobile applications and Internet of Things (IoT) devices, we generate vast quantities of data on a daily basis, often without even realizing it. In this data-driven world, privacy has emerged as a fundamental right that needs to be protected, with individuals concerned about how their personal information is being used and who has access to it. At the same time, organizations worldwide have been grappling with the challenges and opportunities presented by digital transformation, striving to balance the benefits of data-driven innovations with the need to secure sensitive information and protect user privacy. This has led to the development of stringent data protection regulations, such as the European Union’s General Data Protection Regulation (GDPR), as well as the adoption of cutting-edge technologies like blockchain to enhance data security and privacy. In this exclusive interview, Maheen Zaidi, Co-founder of CyberNode AI Lab and Vice President of C3 Cyber Club Community, sits down with Global Security and Risk Magazine (GSARM) to discuss the complexities of digital surveillance and data collection in the modern era, as well as the potential of blockchain technology to address privacy and security concerns in cybersecurity practices. Alongside her, Mr. Ankur Pandey, CEO of CyberNode and Founder of C3 Cyber Club, and Mr. Ahmad Nawaz, Co-founder of both C3 Cyber Club and CyberNode AI Lab, share their insights on the importance of privacy in today’s digital landscape and how blockchain could play a pivotal role in shaping the future of cybersecurity. Unraveling the Challenges of Digital Surveillance and Data Collection The conversation begins with a discussion on the pervasive nature of digital surveillance and data collection in the contemporary world. Maheen elaborates on how advanced technologies, coupled with the Internet’s omnipresence, have made it increasingly difficult for individuals to maintain control over their personal and sensitive information. She notes that despite the convenience and opportunities provided by the digital ecosystem, users are often unaware of the amount of data being collected about them and how it is being used by organizations, governments, and other entities. Adding to this, Mr. Pandey highlights the issue of data breaches, emphasizing the role of cybersecurity in safeguarding users’ information. He underscores the importance of implementing robust security measures to prevent unauthorized access to sensitive data and protect it from malicious actors. He also points out that the lack of transparency in data handling practices can exacerbate privacy concerns, leading to mistrust among users and negatively impacting the reputation of organizations that fail to address these issues. Mr. Nawaz, on the other hand, tackles the topic of surveillance capitalism – a term coined by Shoshana Zuboff to describe the monetization of personal data by corporations. He explains how companies collect vast amounts of information about individuals’ behaviors, preferences, and online activities, subsequently leveraging this data to generate profits through targeted advertising and other business practices. Mr. Nawaz argues that while such practices can provide value to businesses and consumers alike, they also raise ethical concerns, particularly when it comes to issues of privacy and consent. Exploring Blockchain Technology’s Role in Enhancing Security and Privacy Delving into the potential of blockchain technology to address the challenges of digital surveillance and data collection, Maheen explains how its key features – including decentralization, immutability, and transparency – can be harnessed to strengthen security and privacy in cyberspace. She postulates that by enabling individuals to have greater control over their data and ensuring that it is stored securely on a distributed ledger, blockchain can help mitigate risks associated with unauthorized access and data breaches. Mr. Pandey elaborates on this by providing an overview of specific use cases where blockchain can revolutionize data protection, such as secure identity management, encrypted messaging, and secure data sharing. For instance, he suggests that blockchain-based platforms could allow users to create decentralized digital identities that are verifiable and tamper-proof, thereby reducing the risk of identity theft and fraud. Similarly, blockchain-based messaging systems could offer end-to-end encryption, enabling users to communicate privately without the fear of their conversations being intercepted or accessed by third parties. Building upon these ideas, Mr. Nawaz highlights the role of blockchain in tackling surveillance capitalism. He believes that blockchain-powered solutions, such as decentralized applications (dApps), could empower users to regain control of their personal data and decide who can access it, rather than having their information harvested and monetized by corporations. In doing so, blockchain technology can help address the ethical concerns surrounding data collection and usage, while simultaneously fostering greater trust and transparency in the digital ecosystem. The Way Forward: Striking a Balance Between Privacy and Convenience As the interview draws to a close, the trio reflects on the importance of finding the right balance between privacy and convenience in the digital age. They emphasize that while prioritizing privacy and security is crucial, it is also vital for organizations to continue innovating and leveraging the power of data-driven technologies to deliver value to users. For this reason, they suggest that the adoption of blockchain solutions should be conducted in a thoughtful and measured manner, taking into consideration the unique needs and challenges of various industries and stakeholders. Maheen concludes by reiterating the need for collaboration among all key players – including governments, businesses, and individuals – in order to address the complexities of digital surveillance and data collection effectively. She advocates for the establishment of clear and comprehensive policies and regulations that prioritize user privacy and security, coupled with ongoing education and awareness campaigns to ensure that people are well-informed about their rights and responsibilities in the digital world. By working together to harness the potential of blockchain technology and other emerging tools, the panel believes that society can navigate the intricacies of the modern digital landscape and build a secure, privacy-preserving future for all. Conclusion The exclusive interview with Maheen Zaidi, Mr. Ankur Pandey, and Mr. Ahmad Nawaz provides valuable insights into the pressing issue of privacy in the digital age, offering a compelling perspective on how blockchain technology can enhance security and privacy in cybersecurity practices. By unraveling the complexities of digital surveillance and data collection, as well as exploring the potential of blockchain-based solutions, the conversation sheds light on the importance of safeguarding personal and sensitive information in an increasingly connected world. Moreover, the discussion emphasizes the need for collaborative efforts to strike the right balance between privacy and convenience, underscoring the role of governments, organizations, and individuals in shaping the future of digital privacy and security. As the world continues to grapple with the challenges and opportunities presented by the digital revolution, the insights shared by Maheen, Mr. Pandey, and Mr. Nawaz serve as a timely reminder of the need to prioritize privacy rights and harness emerging technologies to create a secure and privacy-preserving digital ecosystem for all.# " ], "headline": "Discover the Essence of Kyoto: Traditional Crafts and Workshops", "author": {"@type": "Person", "name": "The Kyoto Blog"}, "datePublished": "2023-03-01", "description": "Immerse yourself in the world of Kyoto's traditional crafts. From kimonos to pottery, explore workshops where you can learn from skilled artisans and take home a piece of Kyoto's heritage.", "image": "kyoto-craft-workshop.jpg" } } , "mainEntityOfPage": { "@type": "WebPage", "@id": "https://kyotoblog.com/discover-essence-kyoto-traditional-crafts-and-workshops" } }