 { "content": "\\documentclass{article}\n\\usepackage{graphicx}\n\\usepackage{hyperref}\n\\usepackage{enumitem}\n\n\\begin{document}\n\n\\title{Vozz Rich – Electronic Press Kit (EPK)}\n\\author{}\n\\date{}\n\n\\maketitle\n\n\\section*{🎤 Artist Overview}\nVozz Rich is a dynamic producer and DJ who masterfully blends influences from Detroit house, underground raves, salsa, techno, and big room sounds. With roots in Mexico and California, Vozz Rich creates a vibrant fusion of cultural beats and energetic rhythms that ignite dance floors worldwide. His recent collaborations with artists like L25, Kicevski, and Franz Kolo showcase his versatility and growing presence in the electronic music scene. With over 4,100 Spotify followers and consistent streaming growth, Vozz Rich is a rising star in the global dance music community. 🌍🎶\n\n\\section*{📊 Performance \\& Draw}\n\\begin{itemize}\n  \\item \\textbf{Streaming Numbers}: Averaging over 25,000 monthly Spotify listeners, with steady growth across platforms.\n  \\item \\textbf{Social Media Engagement}: 4,862 Instagram followers and strong community engagement rates.\n  \\item \\textbf{Geographic Popularity}: Dominant traction in the US, with growing interest in Latin America and Europe.\n\\end{itemize}\n\n\\section*{🎧 Recent Releases \\& Press}\n\\begin{itemize}\n  \\item \\textbf{Original Tracks}:\n    \\begin{itemize}\n      \\item \"Breathless\" (with L25) – A high-energy house anthem.\n      \\item \"House Ablaze\" (December 2024) – A captivating dance track.\n    \\end{itemize}\n  \\item \\textbf{Top Remixes}:\n    \\begin{itemize}\n      \\item \"Butterflies – Vozz Rich Remix\" by Artsychoke.\n      \\item \"Sofi Disco – Vozz Rich Extended Remix\" by PAUL PARKER.\n    \\end{itemize}\n  \\item \\textbf{Playlist Features}: Included in curated electronic music playlists on Spotify and Apple Music.\n\\end{itemize}\n\n\\section*{🎪 Stage Experience \\& Technical}\n\\begin{itemize}\n  \\item \\textbf{Performance Style}: High-energy DJ sets blending house, techno, and Latin-inspired beats.\n  \\item \\textbf{Technical Rider}: Professional DJ equipment setup required (e.g., Pioneer CDJ-2000 Nexus or equivalent with DJM mixer).\n  \\item \\textbf{Past Events}: Electrifying performances at underground venues and festivals.\n\\end{itemize}\n\n\\section*{📞 Contact \\& Booking}\n\\begin{itemize}\n  \\item \\textbf{Booking Contact}: Richard Park\n    \\begin{itemize}\n      \\item Email: \\href{mailto:vozzrich@gmail.com}{vozzrich@gmail.com}\n      \\item Phone: +1 (310) 989-8178\n    \\end{itemize}\n  \\item \\textbf{Streaming Links}:\n    \\begin{itemize}\n      \\item Spotify: \\href{https://open.spotify.com/artist/27sSKrytmUXukDnMGPXNHQ}{Spotify Profile}\n      \\item SoundCloud: \\href{https://soundcloud.com/user-322739985}{SoundCloud Profile}\n      \\item Apple Music: \\href{https://music.apple.com/us/artist/vozz-rich/1675984686}{Apple Music Profile}\n    \\end{itemize}\n  \\item \\textbf{Website}: \\href{https://vozzrich.com}{vozzrich.com}\n  \\item \\textbf{Social Media}:\n    \\begin{itemize}\n      \\item Instagram: \\href{https://instagram.com/vozzrich}{@vozzrich}\n    \\end{itemize}\n\\end{itemize}\n\n\\vspace{1cm}\n\\noindent \\textbf{Elevate your event with the magnetic sounds of Vozz Rich!} 🚀🎶\n\n\\end{document}\n", "role": "assistant" }